---
title: "bulk_processor-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bulk_processor-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#bulk_processor function

## Purpose

Run all the analysis functions that produce summary graphs for the whole area
covered and save the results in standardised folders.

## Variables

### raster_path 
The filepath for the raster that is to be used. This is compatible with folders containing multiple raster layers

### shapefile_path 
The filepath for the shapefile to be used

### data_path 
The filepath to a folder containing the additonal data

### pollutant 
The pollutant being investigated, this should be in quotes and correspond with its name in the data

### pollutant_data_name
what the pollutant is referred to as in the raw data, should be quoted

### year
The year the data is from, used to standardise column names, currently doesn't work for years before 2000

### prawn_path 
The filepath for the prawn CSV that is to be used.

### pollutant 
The name of the pollutant that's being examined, this is used in the graph names

### version_number 
The version of the package used, this is used when naming the output folder and aids in reproducibility

## Output structure
The name of the folder created is `paste0(pollutant,"_emissions_in_",year,"_v",iteration)` this contains graphs created using the other functions as well as two other subfolders ("Londonless" and "na is 0") which contain the same graphs but without London and with na valsue set to 0 respectively

## Example code
```{r setup,eval=FALSE}
library(PRAWNS)
Startup()
```

``` {r,eval=FALSE}
bulk_processor(raster_path = "Data/pm2.5_rasters_2019",
               shapefile_path = "Data/2011_LSOA_shapefile_20m_generalised",
               data_folder = "Data/LSOA_statistics",
               pollutant_data_name = "pm2_5",
               year = 2019,
               pollutant = "PM2.5",
               iteration="0.3.0")
```
