---
title: "city_processor_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{city_processor_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# city_processor function

## Purpose
This function produces a graphic summarising the emissions in a city with tiled graphs. it requires a PRAWN csv and an LSOA tagged shapefile to work

## Variables

### prawn_path 
The filepath for the prawn CSV that is to be used.

### shape_path 
The filepath for the shapefile that is to be used

### targets 
The name of the thing you're trying to isolate e.g. "Manchester" can also be a vector of valid values

### pollutant 
The name of the pollutant that's being examined, this is used in the graph names

### output_path 
The filepath to output to, a folder will be created at this location which contains all the graphs produced by this code. Defaults to FALSE

## Output structure
This function returns a single image file consisting of tiled graphs
```{r setup,eval=FALSE}
library(PRAWNS)
Startup()
create_prawns(raster_path= "Data/NOx_rasters_2019",
              shapefile_path = "Data/2011_LSOA_shapefile_20m_generalised",
              data_path= list.files("Data/LSOA_statistics"),
              key_variable = "LSOA19CD",
              key_variable_aliases =c("LSOA.code..2011.","?..LSOA11CD"),
              output_path="Outputs/create_prawns_1_0_0_test.csv",
              pollutant_data_name = "nox",
              year=2019,
              pollutant="NOx")
```
```{r,eval=FALSE}
city_summary(prawn_path = "Outputs/create_prawns_1_0_0_test.csv",
                   shape_path = "Data/2011_LSOA_shapefile_20m_generalised",
                   targets = "London",
                   output_path= "Outputs/geographic_summary1_0_0_test",
                    pollutant="NOx"
                  )
```
